---
title: "Blog 2: COVID-19 in Belarus"
description: |
  COVID-19 in Belarus.
author:
  - name: Yezi He
    affiliation: Monash University
date: 09-17-2020
output:
  distill::distill_article:
    self_contained: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, fig.align = 'center')
```

```{r package}
library(tidyverse)
library(tidycovid19)
library(ggplot2)
library(gganimate)
library(hrbrthemes)
library(gifski)
library(plotly)
```

```{r belarus}
belarus1 <- download_jhu_csse_covid19_data(cached = TRUE, silent = TRUE) %>%
  filter(country == "Belarus") %>%
  filter(date > "2020-02-27")
belarus2 <- read_csv(here::here("data/owid-covid-data.csv")) %>%
  filter(location == "Belarus") %>%
  filter(date > "2020-02-27")
```

# Introduction

The COVID-19 pandemic is considered as one of the greatest challenges that the humankind faced. The COVID-19 has fundamentally changed many things. With the measures the governments of many countries taken to contain the spread of COVID-19,the way people move within the country has been restricted. 

# COVID-19 pandemic in Belarus

The first case in Belarus is confirmed on 28 February 2020. 

#As of 2 September 2020, Panama reported 94,084 cases, 2,030 deaths, and 67,487 recoveries. You can select the "Date" and other columns to see cases in particular time period.

Figure \@ref(fig:p1) shows the changes of COVID-19 cases in Belarus more intuitively.The number of confirmed cases in Belarus continues to increase, but the growth trend of the number of recovered people is also very high.

```{r p1,fig.cap="The Covid-19 cases of confirmed, deaths and recovered in Belarus"}
p1 <- belarus1 %>%
  pivot_longer(c(confirmed,deaths,recovered), names_to = "type", values_to = "cases") %>%
  ggplot(aes(x = date, y = cases, color = type)) +
  geom_line() +
  geom_point() +
  theme_ipsum() +
  theme(legend.title = element_blank()) +
  ggtitle("The spread of Covid-19 in Belarus")
  transition_reveal(date)
animate(p1, renderer = gifski_renderer())
anim_save(filename = "changes-belarus.gif")
```



# Data Resources

* Center for Systems Science and Engineering (CSSE) at Johns Hopkins University: https://github.com/CSSEGISandData/COVID-19

