---
title: "Blog 2: COVID-19 in Belarus"
description: |
  COVID-19 in Belarus.
author:
  - name: Yezi He
    affiliation: Monash University
date: 09-17-2020
output:
  distill::distill_article:
    self_contained: false
bibliography: references.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, fig.align = 'center')
```

```{r package}
library(tidyverse)
library(tidycovid19)
library(ggplot2)
library(gganimate)
library(gifski)
library(scales)
library(plotly)
```

```{r belarus}
belarus <- download_jhu_csse_covid19_data(cached = TRUE, silent = TRUE) %>%
  filter(country == "Belarus") %>%
  filter(date > "2020-02-27")
```

# Introduction

The COVID-19 pandemic is considered as one of the greatest challenges that the humankind faced. This blog aims to analysis the spread of COVID-19 in Belarus. This blog mainly used the package *tidycovid19* @tidycovid19 as data resources, including the data from *owidcoronavius* @owidcoronavirus and Center for Systems Science and Engineering (CSSE) @CSSE.

# The spread of coronavirus in Belarus

It is reported that the first case of COVID-19 in Belarus was registered in Minsk on 28 February 2020 @kolodyazhnyy_2020. 

Figure \@ref(fig:p1) shows that the number of confirmed cases in Belarus has increased rapidly since April, and the growth rate has slowed slightly in June. According to the report by TUT.BY @tut.by20201, the reason why there is a small number of confirmed cases before April is that the Health Ministry did not provide reliable information and data on the spread of COVID-19 in the country. But the good thing is that the number of recovered cases also increases at the same time and the number of death cases has remained below 1,000. 

```{r p1,fig.cap="The Covid-19 cases of confirmed, deaths and recovered in Belarus"}
p1 <- belarus %>%
  pivot_longer(c(confirmed,deaths,recovered), names_to = "type", values_to = "cases") %>%
  ggplot(aes(x = date, y = cases, color = type)) +
  geom_line() +
  geom_point() +
  theme_light() +
  xlab("Date") + ylab("Cases") +
  theme(legend.title = element_blank()) +
  ggtitle("The spread of Covid-19 in Belarus") +
  transition_reveal(date) +
  scale_x_date(date_breaks = "1 month", labels=date_format("%b"))
animate(p1, renderer = gifski_renderer())
anim_save(filename = "changes-belarus.gif")

```

# Testing to prevent the spread of the virus

Testing is an important way to properly monitor and prevent the spread of the virus.

```{r dates, fig.cap="The total tests in Belarus with colors of positive rate (%)"}
belarus_test <- download_owid_testing_data(cached = TRUE, silent = TRUE) %>%
  filter(iso3c == "BLR") %>%
  merge(belarus, by.x = "date", by.y = "date") %>%
  select(date, total_tests, confirmed) %>%
  mutate(positive_rate = confirmed/total_tests*100)

dates <- belarus_test %>%
  filter(positive_rate > 7) %>%
  summarise(from = min(date),
            to = max(date))
  
```


```{r p2, fig.cap="The total tests in Belarus with colors of positive rate (%)"}
p2 <- belarus_test  %>%
  ggplot() +
  geom_path(aes(x = date, y = total_tests, color = positive_rate),size = 1.5) +
  geom_path(aes(x = date, y = confirmed, color = positive_rate), size = 1.5) +
  scale_fill_gradient(low="green", high="red")+
  theme_light() +
  ggtitle("Total tests and confirmed cases in Belarus with positive rate") +
  scale_x_date(date_breaks = "1 month", labels=date_format("%b")) +
  xlab("Date") + ylab("Cases/Tests") + labs(color = "Positive Rate (%)") +
  scale_color_gradient(low="green", high="red") +
  geom_rect(data = dates, aes(xmin = from, xmax = to, ymin = -Inf, ymax = Inf), alpha = 0.1, fill = "red") +
  annotate(geom = "text", x=as.Date('2020-09-01'), y=150000, label="Confirmed Cases", size = 3) +
  annotate(geom = "text", x=as.Date('2020-09-01'), y=1400000, label="Total tests", size = 3) +
  annotate(geom = "text", x=as.Date('2020-05-22'), y=1800000, label="Positive rate over 7%", size = 3)
p2

```

On 11 April, the leader of the WHO mission in Belarus, Patrick O'Connor noted the presence of the testing laboratories and improvements of the testing process @tut.by20202. Thus the total tests increased rapidly. 

In Figure \@ref(fig:p2), the slope of the **Total Tests** line is very stable. The colors on the two lines represent the **Positive Rate**, and the red part represents the positive rate greater than 7%. This may be due to the delay in the statistics of the Belarusian government before May 11. After June 18, as the number of tests increases, the positive rate gradually decreases.

